\thetitle

### 2023-06-08 frontmatters.tex
Fixing page number
Fixing format.
Fix typo.

% Title Page
\pagenumbering{roman}

@@

\setcounter{page}{1}

@@

Ende Jin was the sole author of \cref{sec:complete-fmltt}, which were written under the supervision of Prof. Yizhou Zhang.

@@

I am grateful to the reviewers for their many useful comments.  I thank
Benjamin Delaware,
Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, Zhixuan Yang, Prabhakar Ragde, Werner Dietl
for valuable discussions and feedback. I also thank my advisors: Yizhou Zhang and Ondřej Lhoták for their patience and guidance.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the author and do not necessarily
reflect the position of any funding agency.

>>>>

\pagenumbering{gobble}

% Title Page

@@

\newpage
\pagenumbering{roman}
\setcounter{page}{2}

@@

Ende Jin was the sole author for \cref{sec:complete-fmltt}, which were written under the supervision of Prof. Yizhou Zhang.

@@

I am grateful for many useful comments and suggestions.  I thank
Benjamin Delaware,
Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, Zhixuan Yang, Prabhakar Ragde, Werner Dietl
for valuable discussions and feedback.

I also thank my advisors: Yizhou Zhang and Ondřej Lhoták for their patience and guidance.

This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the author and do not necessarily
reflect the position of any funding agency.
